### 2012-03-30 paper.tex
Added decision letter and referee reports from Econometrica

\documentclass[11pt]{article}
%\linespread{1.2}\selectfont
\usepackage{tikz}
\usetikzlibrary{calc}
\usetikzlibrary{fit}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[round,comma]{natbib}
\usepackage{setspace,amsmath,amssymb,amsthm,ifthen,subfig,url,multicol}
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{\thepage}\chead{}\rhead{}
\lfoot{}\cfoot{}\rfoot{}
\renewcommand\headrulewidth{0pt}
\onehalfspacing
\usepackage[margin=1in]{geometry}
\usepackage{nath}

@@

\newcommand{\citepos}[1]{\citeauthor{#1}'s \citeyearpar{#1}}
\newcommand{\Citepos}[1]{\Citeauthor{#1}'s \citeyearpar{#1}}

@@

\newcommand{\oost}{\ensuremath{\operatorname{oos-t}}}
\newcommand{\oosSum}[2]{\ensuremath{\sum_{#1=R-\h+#2}^{T-\h}}}

@@

\newcommand{\CenteredAverage}{\frac{\oosA - \E_T\oosT}{\hat\sigma / \sqrt{P}}}
\newcommand{\CenteredAverageI}{\ensuremath{\frac{1}{\hat\sigma
    \sqrt{P}}\oosSum{t}{1} (D_{tR} - \E_R D_{tR})}}
\newcommand{\CenteredAverageII}{\ensuremath{\frac{\sqrt{P}}{\hat\sigma}
    (\E_R\oosA - \E_T\oosB)}}

\newcommand{\MixingaleArray}[1]{\ensuremath{}}

@@

\newcommand{\couplingConstant}{\ensuremath{2^{\frac{1+\rho}{\rho}} B_L}}
\newcommand{\couplingBeta}[1]{\ensuremath{\beta^{\frac{\rho-2}{2\rho}}_{#1}}}
\newcommand{\couplingBetaSq}[1]{\ensuremath{\beta^{\frac{\rho-2}{\rho}}_{#1}}}
\newcommand{\couplingBound}[1]{\couplingConstant \couplingBeta{#1}}

@@

\frenchspacing \title{Out-of-Sample Comparisons of Overfit Models}
\author{Gray Calhoun\thanks{email: \texttt{gcalhoun@iastate.edu}. I
    would like to thank Julian Betts, Helle Bunzel, Marjorie Flavin,
    Nir Jaimovich, Lutz Kilian, Michael McCracken, Seth Pruitt, Ross
    Starr, Yixiao Sun, Allan Timmermann, participants at the 2010
    Midwest Economics Association Annual Meetings, the 2010
    International Symposium on Forecasting, the 2010 Joint
    Statistical Meetings, and in many seminars at \textsc{ucsd}, and
    espeically Graham Elliott for their valuable suggestions, feedback
    and advice in writing this paper.  I would also like to thank Amit
    Goyal for providing computer code and data for his 2008 RFS paper
    with Ivo Welch \citep{GoW:08}.} \\ Iowa State University,
  Economics Department}
\date{October 24, 2011}

@@

\begin{abstract}\thispagestyle{empty}\noindent
  This paper uses dimension asymptotics to study why overfit linear
  regression models should be compared out-of-sample; we let the
  number of predictors used by the larger model increase with the
  number of observations so that their ratio remains uniformly
  positive.  Under this limit theory, the naive Diebold-Mariano-West
  out-of-sample test can test hypotheses about a key quantity for
  evaluating forecasting models---a time series analogue to the
  generalization error---as long as the out-of-sample period is small
  relative to the total sample size.  Moreover, tests that are
  designed to reject if the larger model is true, such as the usual
  in-sample Wald and \textsc{lm} tests and also Clark and McCracken's
  (2001, 2005a), \citepos{Mcc:07}, and Clark and West's (2006, 2007)
  out-of-sample statistics, will choose the larger model too often
  when the smaller model is more accurate.

\noindent \textsc{jel} Classification: C01, C12, C22, C52, C53

@@

\section{Introduction}\label{sec:introduction}
Consider two sequences of length $P$ of prediction errors, the result
of forecasting the same variable with two different estimated models.
Both models are estimated with $R$ observations, collectively called
the {\em estimation window}, and are used to forecast an additional
$P$ observations, called the {\em test sample}.  There are $T$
observations in all, and $R+P=T$.  This paper introduces a new limit
theory for statistics constructed from these prediction errors
designed to approximate the behavior of the statistics when one of the
models is overfit.  In doing so, we provide a theoretical
justification for forecasters to use \oos\ instead of
in-sample comparisons.

Although \oos\ comparisons have been popular in macroeconomics and
finance since \citepos{MeR:83} seminal study of exchange rate models,
it is unclear from a theoretical perspective whether or not the
statistics are useful.  Empirical researchers often cite ``overfit''
or ``instability'' as reasons for using \oos\ comparisons, as in
\citet{StW:03}, but neither term is precisely defined or formalized.
Compounding this problem, the asymptotic distributions of these
statistics are derived under conditions that rule out either
instability or overfit and allow a researcher to use a conventional
in-sample comparison---a variation of the F-test, for example.  As
\citet{InK:04} argue, the statistics themselves are designed to test
hypotheses that can be tested by these in-sample statistics.  For
example, \citet{DiM:95} and \citet{Wes:96} derive the limiting
distributions of many popular \oos\ test statistics under conditions
that would justify these full-sample tests.\footnote{In this paper, we
  will refer to their basic \oos\ $t$-test as the \dmw\ test.}  Much
of the subsequent research by \citet{Mcc:00, Mcc:07}, \citet{CCS:01},
\citet{ClM:01,ClM:05}, \citet{CoS:02,CoS:04}, \citet{ClW:06,ClW:07},
\citet{Ana:07}, and others relaxes several of Diebold and Mariano's
and West's assumptions, but maintains the stationarity and dependence
conditions that permit in-sample comparisons.\footnote{Like us,
  \citet{Ana:07} allows the number of regressors to increase with $T$.
  But in that paper, they increase slowly enough that the \ols\
  coefficients are consistent and asymptotically normal.}
\citet{GiW:06}, and \citet{GiR:09, GiR:10} are exceptions.  Instead of
focusing on hypotheses that can be tested by in-sample comparisons,
\citet{GiW:06} derive an \oos\ test for the null hypothesis that the
difference between two models' \oos\ forecasting performance is
unpredictable, a martingale difference sequence; \citet{GiR:09} test
whether the \oos\ forecasting performance of a model suffers from a
breakdown relative to its in-sample performance; and \citet{GiR:10}
test whether the forecasting performance is stable. However, those
papers focus on a particular \oos\ estimation strategy and do not
address why naive \oos\ comparisons might be generally useful.

@@

In this paper, we study the ``overfit'' possibility and leave
``instability'' to future research. This paper uses dimension
asymptotics to study the behavior of \oos\ comparisons when at least
one of the models is overfit---when the number of its regressors
increases with the number of observations so that their ratio remains
positive.  We focus on linear regression models estimated with a fixed
training window, but our basic conclusions should be true for other
estimation strategies and models as well.  Under this asymptotic
theory, the \ols\ coefficient estimator is no longer consistent or
asymptotically normal \citep{Hub:73} and has positive variance in the
limit.  Even so, we show that the usual \oos\ average is
asymptotically normal and can consistently estimate the difference
between the models' expected loss in periods $T+1,T+2,\dots$
conditional on the on the data available in period $T$, a time-series
analogue to the generalization error.\footnote{See, for example,
  \citet{HTF:08}.}  Under these asymptotics, the generalization error
does not converge to the expected performance of the pseudo-true
models, so the in-sample and \oos\ comparisons measure different
quantities and should be expected to give different results for
reasons beyond simple size and power comparisons.  Under our theory,
the model that is closer to the true \dgp\ in population can forecast
worse.  In such a situation, an in-sample comparison would correctly
reject the null hypothesis that the benchmark is true, and an \oos\
comparison would correctly fail to reject the null that the benchmark
is more accurate.\footnote{In a pair of papers similar to ours,
  \citet{ClM:09,ClM:09b} study in-sample and \oos\ tests that the
  larger model has nonzero coefficients that are too close to zero to
  expect the model to forecast more accurately.  Like this paper, they
  argue that the larger model can be true but less accurate.  However,
  they focus on an aspect of the \dgp\ that makes this phenomenon
  likely, while we focus on the coefficient estimates that produce
  less accurate forecasts.}

This result justifies \oos\ comparisons when researchers want to
choose a model for forecasting.  Although there has been little
emphasis on hypothesis testing in this setting, testing is usually
appropriate: there is usually a familiar benchmark model in place, and
the cost of incorrectly abandoning the benchmark for a less accurate
alternative model is higher than the cost of incorrectly failing to
switch to a more accurate alternative.\footnote{These costs can be
  monetary, in the form of computer upgrades, software installation,
  and training, or they can be reputational costs.}
We show that the \dmw\ test lets the forecaster control the
probability of the first error, just as with conventional hypothesis
testing.

Since the models' coefficients are imprecisely estimated in the limit,
the test sample must be small to ensure that the model estimated over
the training sample is similar to the one that will be estimated over
the full sample.  In particular, $P/T \to 0$ is required for
consistent estimation, and $P^2/T \to 0$ is required for valid
confidence intervals and inference.  For larger $P$, the \oos\
comparisons remain asymptotically normal, but are centered on the
forecasting performance associated with the period-$R$ estimates.  In
practice, researchers typically use large values of $P$, so these
studies may be too pessimistic about their models' future accuracy if
they use the \dmw\ test.  Section~\ref{sec:oostheory} lays out the
asymptotic behavior of the \dmw\ test under this limit theory.

Since the \ols\ coefficient estimator is no longer consistent or
asymptotically normal, the F-test and Wald tests are no longer
asymptotically valid.  Moreover, \citet{Efr:86,Efr:04} shows that
naive comparisons of in-sample loss overestimate models' accuracy by a
factor proportional to $K/T$, $K$ being the number of regressors.  But
modifications of the F-test are valid under this asymptotic theory, as
shown by \citet{BoB:95}, \citet{AkA:00}, \citet{AkP:04}, and
\citet{Cal:10}, among others.  Such results establish that hypotheses
about the parameters of the \dgp\ can be tested in-sample even if one
or both models are overfit.  For that very reason, these tests can not
reliably choose a model for forecasting and will reject the benchmark
too often.  We show this analytically in Section~\ref{sec:insample}.
Moreover, under this asymptotic theory, many recent \oos\ test
statistics, such as those derived by \cite{ClM:01,ClM:05},
\citet{Mcc:07}, and \citet{ClW:06,ClW:07} should behave like the
F-test.  These tests are also designed to reject the benchmark when
the alternative model is true, and so they may reject too often when
the benchmark is false but more accurate.  Obviously, since the
distribution of these statistics converges to the normal when $P/T \to
0$ (with the number of regressors fixed), these statistics behave like
the \dmw\ test when $P$ is small, but should over-reject the benchmark
when $P$ is large.  Section~\ref{sec:mc} presents simulations that
support these claims.

Finally, this paper also introduces a new method of proof for \oos\
statistics.  We use a coupling argument (Berbee's Lemma, 1979) to show
that sequences of \oos\ loss behave like mixingales when the
underlying series are absolutely regular, even if the forecasts depend
on non-convergent estimators.  Moreover, transformations of these
processes also behave like mixingales, so asymptotic results for \ned\
functions of mixing processes can be used for these \oos\ processes
with only slight modification.  Although we only present a proof that
this mixingale result holds for the fixed-window scheme, it is simple
to extend it to other estimation windows.

@@

\section{Setup and Assumptions}\label{sec:assumptions}
We will set up our models and notation first, then list the assumptions
required for our results.  There are two competing linear models that
give forecasts for the target, $y_{t+\h}$:
\[
y_{t+\h} = x_{1t}'\theta_1 + \varepsilon_{1,t+h}
\]
and
\[
y_{t+\h} = x_{2t}'\theta_2 + \varepsilon_{2,t+h};
\]
$\h$ is the forecast horizon, and the variables $y_t$, $x_{1t}$, and
$x_{2t}$ are all known in period $t$.  Let
\begin{equation*}
  \mathcal{F}_t = \sigma(y_1, x_1, \dots, y_t, x_t)
\end{equation*}
with $x_t$ the vector of all elements of $x_{1t}$ and $x_{2t}$ after
removing duplicates, and let $\E_t$ and $\var_t$ denote the
conditional mean and variance given $\mathcal{F}_t$.  The first model
uses $K_1$ regressors, and the second uses $K_2$.  Without loss of
generality, assume that $K_1 \leq K_2$.  We will allow $K_1$ and $K_2$
to vary with $T$, so a stochastic array underlies all of our
asymptotic theory, but we suppress that notation to make the
presentation more clear.

Although our theory can apply to many different \oos\ statistics,
we'll only present results for the \dmw\ \oos\ $t$-test.  Both models
are estimated using \ols\ over the training sample:
\[
\hat y_{i,t+\h} = x_{it}'\bh{iR}, \quad i=1,2, \quad t = R+1,\dots,T-h
\]
with
\[
\bh{it} = (\sum_{s=1}^{t-\h} x_{is}x_{is}')^{-1} \sum_{s=1}^{t-\h} x_{is} y_{s+\h},
\quad i=1,2.
\]
The \oos\ average is denoted $\oosA$:
\[
\oosA \equiv P^{-1} \oosSum{t}{1} D_{tR}
\quad \text{with} \quad D_{tS} \equiv L(y_{t+\h} - x_{1t}'\bh{1S}) -
L(y_{t+\h} - x_{2t}'\bh{2S}),
\]
$P = T - R$ and $L$ a known loss function.  The \oos\ statistic
of interest is 
\[
\oost \equiv \frac{\sqrt{P} \oosA}{\hat\sigma},
\]
for $\hat\sigma^2$ some (possibly Heteroskedasticity- and
Autocorrelation-Consistent, or \hac) estimator of the asymptotic
variance of $\oosA$.

We'll show that \oost\ can be used to test whether the models will
forecast equally accurately in the future.  Specifically, assume that
whichever model is chosen will be used for an additional $Q$ periods
in the future and let $\oosB$ denote the difference in average
performance over those periods:
\[
\oosB \equiv Q^{-1} \sum_{t=T+1}^{T+Q} D_{tT}.
\]
Note that $\oosA$ depends on the training sample estimators,
$\hat\theta_{iR}$, and $\oosB$ depends on the full sample
estimators, $\hat\theta_{iT}$.  A forecaster has access to the
information set $\mathcal{F}_T$ when deciding between the two
forecasting models, but $\mathcal{F}_T$ does not contain $\oosB$.
So a forecaster should decide between the models based on the
conditional expectation, $\E_T \oosB$. If this quantity is
positive, the first model is expected to perform worse in the future,
and if it is negative the second is.

When the underlying series is i.i.d., this random variable, $\E_T
\oosB$, is equal to the difference in the models' generalization
error.  The generalization error of model $i$ is defined as
\begin{equation*}
  \E_{T} L(y_{T+\h}^{*} - x_{iT}^{*\prime}\hat{\theta}_{iT})
\end{equation*}
where $(y_{T+\h}^{*},x_{iT}^{*})$ has the same joint distribution as
$(y_{T+\h}, x_{iT})$ but is independent of $\mathcal{F}_T$.  Note that
$\hat{\theta}_{iT}$ is known in period $T$, so the generalization
error conditions on the observed coefficient estimates.  With
dependence, the coefficient estimates may be informative about future
values of $y_{t+\h}$ and $x_{it}$, but this influence dies out as $Q$
grows.  Conditional performance measures like these are especially
appropriate in areas like time-series economics where the forecaster
knows the coefficient values when choosing a model, but would be less
appropriate if the models will be re-estimated over an entirely new
dataset before forecasting.

@@

\begin{asmp}\label{asmp-1} 
  The random array $\{y_t,x_t\}$ is stationary and
  absolutely regular with coefficients $\beta_j$ of size
  $-\rho/(\rho-2)$; $\rho$ is greater than two and discussed further
  in Assumption \ref{asmp-3}.  Also, $K_1$ and $K_2$ are less than $R$,
  and $\frac{K_2}{T}$ and $\frac{K_2-K_0}{T}$ are uniformly positive;
  $K_0$ is the number of regressors shared by the two models ($K_1/T$
  can be uniformly positive as well, but is not required to be).
\end{asmp}

@@

\begin{asmp}\label{asmp-3}
  The loss function $L$ is continuous and has finite left and right
  derivatives almost everywhere.  Also, $L(0) = 0$, and there is a
  constant $B_L$ such that
  \begin{equation*}
    \|D_{R+j,R}\|_\rho \leq B_L \quad\text{and}\quad
    \|D_{T+j,T}\|_\rho \leq B_L.
  \end{equation*}
  for all $j \geq 1$.
\end{asmp}

@@

\begin{asmp} \label{asmp-4} $P\to\infty$,
  $R\to\infty$, $Q\to\infty$, $P^2/T \to 0$, and $P = O(Q)$ as $T \to \infty$.
\end{asmp}

@@

The next assumption restricts the class of variance estimators we will
consider.  We use the same class of estimators studied by
\citet{DeD:00} (their class $\mathcal{K}$); see
their paper for further discussion.

>>>>

\documentclass[11pt]{article}
\usepackage{tikz}
\usetikzlibrary{calc}
\usetikzlibrary{fit}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[round,comma]{natbib}
\usepackage{setspace,amsmath,amssymb,amsthm,ifthen,subfig,url,multicol}
\onehalfspacing\frenchspacing
\usepackage[margin=1in]{geometry}

@@

\newcommand{\citepos}[1]{\citeauthor{#1}'s \citeyearpar{#1}}
\newcommand{\Citepos}[1]{\Citeauthor{#1}'s \citeyearpar{#1}}
\newcommand{\clws}{\citeauthor{ClW:06}'s \citeyearpar{ClW:06,ClW:07}}

@@

\newcommand{\oost}{\ensuremath{\operatorname{oos-t}}}
\newcommand{\oosSum}[2]{\ensuremath{\sum_{#1=R+#2}^{T-\h}}}

@@

@@

\newcommand{\couplingConstant}{\ensuremath{2^{(1+\rho)/\rho} B_L}}
\newcommand{\couplingBeta}[1]{\ensuremath{\beta^{(\rho-2)/2\rho}_{#1}}}
\newcommand{\couplingBetaSq}[1]{\ensuremath{\beta^{(\rho-2)/\rho}_{#1}}}
\newcommand{\couplingBound}[1]{\couplingConstant \couplingBeta{#1}}

@@

\frenchspacing \title{Out-of-Sample Comparisons of Overfit Models}
\author{Gray Calhoun\thanks{email: \texttt{gcalhoun@iastate.edu}. I
    would like to thank Julian Betts, Helle Bunzel, Marjorie Flavin,
    Nir Jaimovich, Lutz Kilian, Ivana Komunjer, Michael McCracken,
    Seth Pruitt, Ross Starr, Jim Stock, Yixiao Sun, Allan Timmermann,
    Hal White, several anonymous referees, participants at the 2010
    Midwest Economics Association Annual Meetings, the 2010
    International Symposium on Forecasting, the 2010 Joint Statistical
    Meetings, and in many seminars at \textsc{ucsd}, and espeically
    Graham Elliott for their valuable suggestions, feedback and advice
    in writing this paper.  I would also like to thank Amit Goyal for
    providing computer code and data for his 2008 RFS paper with Ivo
    Welch \citep{GoW:08}.} \\ Iowa State University}
\date{October 24, 2011}

@@

\begin{abstract}\thispagestyle{empty}\noindent
  This paper uses dimension asymptotics to study why overfit linear
  regression models should be compared out-of-sample; we let the
  number of predictors used by the larger model increase with the
  number of observations so that their ratio remains uniformly
  positive.  Under this limit theory, the naive Diebold-Mariano-West
  out-of-sample test can test hypotheses about the models'
  generalization error, a key quantity for evaluating forecasting
  models.  Moreover, tests that are designed to reject if the larger
  model is true, such as the usual in-sample Wald and \textsc{lm}
  tests and also Clark and McCracken's (2001, 2005a),
  \citepos{Mcc:07}, and Clark and West's (2006, 2007) out-of-sample
  statistics, will choose the larger model too often when the smaller
  model is more accurate.

\noindent \textsc{jel} Classification: C12, C22, C52, C53

@@

\section{Introduction}\label{sec:introduction}
Consider two sequences of length $P$ of prediction errors, the result
of forecasting the same variable with two different estimated models.
Both models are estimated with $R$ observations, collectively called
the {\em estimation window}, and are used to forecast an additional
$P$ observations, called the {\em test sample}.  There are $T$
observations in all, and $R+P=T$.  This paper introduces a new limit
theory for statistics constructed from these prediction errors
designed to approximate the behavior of the statistics when one of the
models is overfit.  In doing so, we provide a theoretical
justification for forecasters to use \oos\ instead of in-sample
comparisons and discover a practical limitation in existing statistics.

Although \oos\ comparisons have been popular in macroeconomics and
finance since \citepos{MeR:83} seminal study of exchange rate models,
it is unclear from a theoretical perspective whether or not the
statistics are useful.  Empirical researchers often cite ``overfit''
or ``instability'' as reasons for using \oos\ comparisons, as in
\citet{StW:03}, but neither term is precisely defined or formalized.
Compounding this problem, the asymptotic distributions of these
statistics are derived under conditions that rule out either
instability or overfit and allow a researcher to use a conventional
in-sample comparison---a variation of the F-test, for example.  As
\citet{InK:04} argue, the statistics themselves are designed to test
hypotheses that can be tested by these in-sample statistics.  For
example, \citet{DiM:95} and \citet{Wes:96} derive the limiting
distributions of many popular \oos\ test statistics under conditions
that would justify these full-sample tests.\footnote{In this paper, we
  will refer to their basic \oos\ $t$-test as the \dmw\ test.}  Much
of the subsequent research by \citet{Mcc:00, Mcc:07}, \citet{CCS:01},
\citet{ClM:01,ClM:05}, \citet{CoS:02,CoS:04}, \citet{ClW:06,ClW:07},
\citet{Ana:07}, and others relaxes several of Diebold and Mariano's
and West's assumptions, but maintains the stationarity and dependence
conditions that permit in-sample comparisons.\footnote{Like us,
  \citet{Ana:07} allows the number of regressors to increase with $T$.
  But in that paper, they increase slowly enough that the \ols\
  coefficients are consistent and asymptotically normal.}
\citet{GiW:06} and \citet{GiR:09, GiR:10} are exceptions.  Instead of
focusing on hypotheses that can be tested by in-sample comparisons,
\citet{GiW:06} derive an \oos\ test for the null hypothesis that the
difference between two models' \oos\ forecasting performance is
unpredictable, a martingale difference sequence; \citet{GiR:09} test
whether the \oos\ forecasting performance of a model suffers from a
breakdown relative to its in-sample performance; and \citet{GiR:10}
test whether the forecasting performance is stable. However, those
papers focus on a particular \oos\ estimation strategy and do not
address why \oos\ comparisons might be useful as a general strategy.

@@

In this paper, we study the ``overfit'' possibility and leave
``instability'' to future research. This paper uses dimension
asymptotics to study the behavior of \oos\ comparisons when at least
one of the models is overfit---when the number of its regressors
increases with the number of observations so that their ratio remains
positive.  Although overfit is sometimes used to describe the
situation where a forecaster chooses from many different models, we
view that as a separate issue.  Procedures that account for the
presence of many models are being developed \citep[see, for
example,][]{Whi:00,RoW:05}, but there is still disagreement about
whether those procedures should themselves use in-sample or \oos\
comparisons.  Understanding this issue in the context of a simple
comparison between two models is necessary before resolving any new
issues that arise with multiple comparisons.

We focus on linear regression models for simplicity, but our basic
conclusions should be true for other estimation strategies and models
as well.  Under this asymptotic theory, the \ols\ coefficient
estimator is no longer consistent or asymptotically normal
\citep{Hub:73} and has positive variance in the limit.  Even so, we
show that the usual \oos\ average is asymptotically normal and can
consistently estimate the difference between the models'
generalization error, the expected loss in the future conditional on
the on the data available in period $T$.\footnote{See, for example,
  \citet{HTF:08}.}  Under these asymptotics, the generalization error
does not converge to the expected performance of the pseudo-true
models, so the in-sample and \oos\ comparisons measure different
quantities and should be expected to give different results for
reasons beyond simple size and power comparisons.  Under our theory,
the model that is closer to the true \dgp\ in population can forecast
worse.  In such a situation, a standard in-sample comparison would
correctly reject the null hypothesis that the benchmark is true, and
an \oos\ comparison would correctly fail to reject the null that the
benchmark is more accurate.\footnote{In a pair of papers similar to
  ours, \citet{ClM:09,ClM:09b} study in-sample and \oos\ tests that
  the larger model has nonzero coefficients that are too close to zero
  to expect the model to forecast more accurately.  Like this paper,
  they argue that the larger model can be true but less accurate.
  However, they focus on an aspect of the \dgp\ that makes this
  phenomenon likely, while we focus on the coefficient estimates that
  produce less accurate forecasts.}

This result justifies \oos\ comparisons when researchers want to
choose a model for forecasting.  Although there has been little
emphasis on hypothesis testing in this setting, testing is usually
appropriate: there is usually a familiar benchmark model in place, and
the cost of incorrectly abandoning the benchmark for a less accurate
alternative model is higher than the cost of incorrectly failing to
switch to a more accurate alternative.\footnote{Because we focus on
  testing relative to a benchmark, rather than model selection with
  now benchmark, we will not discuss in-sample statistics with
  penalties for overparametrization, e.g. the \textsc{aic} or adjusted
  R-square.  \citet{Lee:08} discusses similar issues to ours related
  to model selection.}
We show that the \dmw\ test lets the forecaster control the
probability of the first error, just as with conventional hypothesis
testing.

Since the models' coefficients are imprecisely estimated in the limit,
the test sample must be small enough that the model estimated over
the training sample is similar to the one that will be estimated over
the full sample.  In particular, $P/T \to 0$ is required for
consistent estimation, and $P^2/T \to 0$ is required for valid
confidence intervals and inference.  For larger $P$, the \oos\
comparisons remain asymptotically normal, but are centered on the
forecasting performance associated with the period-$R$ estimates.  In
practice, researchers typically use large values of $P$, so these
studies may be too pessimistic about their models' future accuracy if
they use the \dmw\ test.  Section~\ref{sec:oostheory} lays out the
asymptotic behavior of the \dmw\ test under this limit theory.

Since the \ols\ coefficient estimator is no longer consistent or
asymptotically normal, the F-test and Wald tests are no longer
asymptotically valid.  Moreover, \citet{Efr:86,Efr:04} shows that
naive comparisons of in-sample loss overestimate models' accuracy by a
factor proportional to $K/T$, $K$ being the number of regressors.  But
modifications of the F-test are valid under this asymptotic theory, as
shown by \citet{BoB:95}, \citet{AkA:00}, \citet{AkP:04}, and
\citet{Ana:12}, \citet{Cal:11c}, among others.  Such results establish
that hypotheses about the parameters of the \dgp\ can be tested
in-sample even if one or both models are overfit.  For that very
reason, these tests can not reliably choose a model for forecasting
and will reject the benchmark too often.  We show this analytically in
Section~\ref{sec:insample}.  Moreover, under this asymptotic theory,
many recent \oos\ test statistics, such as those derived by
\cite{ClM:01,ClM:05}, \citet{Mcc:07}, and \citet{ClW:06,ClW:07} should
behave like the F-test.\footnote{Our theoretical results apply
  directly to \citepos{Mcc:07} \oost test, since it simply proposes
  more liberal critical values for the same test statistic.  Since
  \citet{ClW:06,ClW:07} use a finite length estimation window, our
  asymptotics are incompatible with theirs and prevent us from
  studying their test directly, as well as \citepos{GiW:06} and other
  similar tests.  But \clws\ test can be viewed as a stochastic
  adjustment to the critical values of the usual \oost test, so our
  theoretical results should apply informally as well.  Specifically,
  we show that the \dmw\ test rejects probability equal to nominal
  size, so more liberal critical values result in over-rejection.}
These tests are also designed to reject the benchmark when the
alternative model is true, and so they may reject too often when the
benchmark is false but more accurate.  Obviously, since the
distribution of these statistics converges to the normal when $P/T \to
0$ (with the number of regressors fixed), these statistics behave like
the \dmw\ test when $P$ is small, but should over-reject the benchmark
when $P$ is large.  Section~\ref{sec:mc} presents simulations that
support these claims.

Finally, this paper also introduces a new method of proof for \oos\
statistics.  We use a coupling argument (Berbee's Lemma, 1979) to show
that sequences of \oos\ loss behave like mixingales when the
underlying series are absolutely regular, even if the forecasts depend
on non-convergent estimators.  Moreover, transformations of these
processes also behave like mixingales, so asymptotic results for \ned\
functions of mixing processes can be used for these \oos\ processes
with only slight modification.

@@

\section{Setup and Assumptions}\label{sec:assumptions}
We will set up our models and notation first, then list the assumptions
required for our results.  There are two competing linear models that
give forecasts for the target, $y_{t+\h}$:
\[
y_{t+\h} = x_{1t}'\theta_1 + \varepsilon_{1,t+h}, \quad\text{and}\quad
y_{t+\h} = x_{2t}'\theta_2 + \varepsilon_{2,t+h};
\]
$t = 1,\dots,T-h$, $\h$ is the forecast horizon, and the
variables $y_t$, $x_{1t}$, and $x_{2t}$ are all known in period $t$.
Let
\begin{equation*}
  \mathcal{F}_t = \sigma(y_1, x_1, \dots, y_t, x_t)
\end{equation*}
with $x_t$ the vector of all elements of $x_{1t}$ and $x_{2t}$ after
removing duplicates, and let $\E_t$ and $\var_t$ denote the
conditional mean and variance given $\mathcal{F}_t$.  The first model
uses $K_1$ regressors, and the second uses $K_2$.  Without loss of
generality, assume that $K_1 \leq K_2$.  We will allow $K_1$ and $K_2$
to vary with $T$, so a stochastic array underlies all of our
asymptotic theory, but we suppress that notation to make the
presentation more clear.

We assume the following forecasting environment: the forecaster
observs the data $(y_t,x_t)$ for periods 1 through $T$ and divides
them into an estimation sample of the first $R+h$ observations and a
test sample of the remaining $P$ observations.  After choosing one of
the models, the forecaster will use that model to make predictions for
periods $T + h$ through $T + h + Q$, where $Q$ is a known positive
integer.  The forecaster's goal is to choose the model that will have
lower average loss over periods $T+h$ through $T+h+Q$, evaluated by
the known loss function $L$.

Both models are estimated using \ols\ with a recursive, fixed, or
rolling window:
\[
\hat y_{i,t+\h} = x_{it}'\bh{iR}, \qquad i=1,2, \qquad t = R+1,\dots,T-h
\]
with
\begin{equation*}
\bh{it}^{R} = \begin{cases} \big(\sum_{s=1}^{t-\h} x_{is}x_{is}'\big)^{-1}
\sum_{s=1}^{t-\h} x_{is} y_{s+\h} & \text{recursive window}\\
 \big(\sum_{s=t - \h - R}^{t-\h} x_{is}x_{is}'\big)^{-1}
\sum_{s=t - \h - R}^{t-\h} x_{is} y_{s+\h} & \text{rolling window} \\
 \big(\sum_{s=1}^{R-\h} x_{is}x_{is}'\big)^{-1} 
\sum_{s=1}^{R-\h} x_{is} y_{s+\h} & \text{fixed window}
\end{cases}
\end{equation*}
The observed \oos\ average is denoted $\oosA$: \[\oosA \equiv P^{-1}
\oosSum{t}{1} D_{Rt}\]  with
\[
D_{Rt} \equiv L(y_{t+\h} - x_{1t}'\bh{1t}^R) - L(y_{t+\h}
  - x_{2t}'\bh{2t}^R).
\]
The \oos\ statistic of interest is $\oost \equiv \sqrt{P} \oosA /
\hat\sigma$, for $\hat\sigma^2$ some (possibly Heteroskedasticity- and
Autocorrelation-Consistent, or \hac) estimator of the asymptotic
variance of $\oosA$.

As discussed above, the forecaster's goal is to choose the model with
lower average future loss; i.e. to determine whether $\oosB$ is
positive or negative,with
\[
\oosB \equiv Q^{-1} \sum_{t=T+1}^{T+Q} D_{Tt},
\]
with
\[
D_{Tt} \equiv L(y_{t+h} - x_{1t}' \bh{1t}^T) - L(y_{t+h} - x_{2t}' \bh{2t}^T)
\]
and 
\begin{equation*}
\bh{it}^{T} = \begin{cases} \big(\sum_{s=1}^{t-\h} x_{is}x_{is}'\big)^{-1}
\sum_{s=1}^{t-\h} x_{is} y_{s+\h} & \text{recursive window}\\
 \big(\sum_{s=t - \h - T}^{t-\h} x_{is}x_{is}'\big)^{-1}
\sum_{s=t - \h - T}^{t-\h} x_{is} y_{s+\h} & \text{rolling window} \\
 \big(\sum_{s=1}^{T-\h} x_{is}x_{is}'\big)^{-1} 
\sum_{s=1}^{T-\h} x_{is} y_{s+\h} & \text{fixed window}.
\end{cases}
\end{equation*}
Note that the coefficients are reestimated with a larger dataset for
the fixed and rolling windows.  Since the forecaster's information
set, $\mathcal{F}_T$, does not contain $\oosB$, he or she should
decide between the models based on the conditional expectation, $\E_T
\oosB$. If this quantity is positive, the first model is expected to
perform worse in the future, and if it is negative the second is.

This random variable is related to several well known measures of
model performance.  As $Q \to \infty$, it converges to the difference
in the models' generalization error and equals it for i.i.d. data.
Moreover, if the data are i.i.d., the expectation of $\E_T \oosB$
equals \citepos{Aka:69} Final Prediction Error (\textsc{fpe}).  Both
generalization error and \textsc{fpe} are defined as teh performance
on a new, independent, data set; here the new data is not
independent.  Since $Q \to \infty$ in our asymptotic theory, though,
we will call $\E_T \oosB$ the difference in generalization error
throughout the paper with hopefully no risk of confusion.

@@

\begin{asmp}\label{asmp-1} 
  The random array $\{y_t,x_t\}$ is stationary and absolutely regular
  with coefficients $\beta_j$ of size $-\rho/(\rho-2)$; $\rho$ is
  greater than two and discussed further in Assumption \ref{asmp-3}.
  Also, $K_1$ and $K_2$ are less than $R$, and $K_2/T$ and
  $(K_2-K_0)/T$ are uniformly positive; $K_0$ is the number of
  regressors shared by the two models ($K_1/T$ can be uniformly
  positive as well, but is not required to be).
\end{asmp}

@@

\begin{asmp}\label{asmp-3}
  The loss function $L$ is continuous and has finite left and right
  derivatives almost everywhere.  Also, $L(0) = 0$, and there is a
  constant $B_L$ such that
  \begin{equation*}
    \|D_{R,R+j}\|_\rho \leq B_L \quad\text{and}\quad
    \|D_{T,T+j}\|_\rho \leq B_L.
  \end{equation*}
  for all $j \geq 1$; $\rho$ is defined in Assumption~\ref{asmp-1}.
\end{asmp}

@@

\begin{asmp} \label{asmp-4} $P\to\infty$, $R\to\infty$, $Q\to\infty$,
  $P = o(T^{1/2}) + O(Q)$ as $T \to \infty$.  For the rolling and
  recursive windows, $Q = o(T^{1/2})$ as well.
\end{asmp}

@@

The next assumption restricts the class of variance estimators we will
consider.  We use the same class of estimators studied by
\citet{JoD:00} (their class $\mathcal{K}$); see
their paper for further discussion.
